Generating Correlated Data for Omics Simulation

### 2025-05-08 manuscript/supplemental/supplemental.qmd
Add benchmark of runtime + memory usage

>>>>

### Benchmark
```{r}
#| label: fig-benchmark
#| fig-cap: "Comparison of (a) run time and (b) memory usage for our methods and SPsimSeq. 100 samples were generated with a varying number of genes. GSE151564 dataset was randomly subsetted to have the required number of genes to be used as the reference data set."
#| fig-width: 8
#| fig-height: 4
library(tidyverse)
library(patchwork)
METHOD_ORDER <- c("real", "indep", "pca", "wishart", "corpcor", "SPsimSeq")
METHOD_COLORS <- c("black", RColorBrewer::brewer.pal(length(METHOD_ORDER)-1, "Dark2"))
benchmark <- read_tsv("../../processed/benchmark/results.txt")
g1 <- ggplot(benchmark, aes(x=n_genes, y=time, color=method)) +
    geom_line(linewidth=2) +
    labs(x = "N genes", y = "time (seconds)") + 
    scale_color_manual(values = METHOD_COLORS, breaks = METHOD_ORDER, name="method") +
    scale_x_log10() +
    scale_y_log10()
g2 <- ggplot(benchmark, aes(x=n_genes, y=max_rss, color=method)) +
    geom_line(linewidth=2) +
    labs(x = "N genes", y = "memory (MB)") +
    scale_color_manual(values = METHOD_COLORS, breaks = METHOD_ORDER, name="method") +
    scale_x_log10() +
    scale_y_log10()
g1 + g2 + plot_annotation(tag_levels="a") + plot_layout(guides = "collect")
```
